### 2018-01-24 ApproxComp/sec-introduction.tex

Over the past a few years, research and development progresses on big data analytics have made significant achievements with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}. A fundamental issue for big data analytics is the efficiency, and there are different recent advances towards attacking this issues, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.  In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research. Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation techniques that we are going to introduce are not unnecessarily theoretically bounded with respect to optimal solutions, but are practically useful and interesting.

>>>>

Over the past a few years, research and development progresses on big data analytics have made significant achievements with the supports from both governments and industries all over the world, such as Spark\footnote{\small \url{https://spark.apache.org}}, IBM Watson\footnote{\small \url{https://www.ibm.com/watson}} and Google AlphaGo\footnote{\small \url{https://deepmind.com/research/alphago}}. A fundamental issue for big data analytics is the efficiency, and there are different recent advances towards attacking this issues, from theory to algorithms to platforms~\cite{FanGN13,Jordan15,ZahariaXWDADMRV16}.  In this article, we shall present the idea of two classes of techniques for efficient and effective big data analytics: query approximation and data approximation, based on our recent research. Different from existing approximation techniques~\cite{CormenLRS01,approx03,FanH14}, the approximation computation that we are going to introduce is not unnecessarily theoretically bounded with respect to optimal solutions, but are practically useful and interesting.

### 2018-01-24 ApproxComp/sec-query.tex

\stitle{(3) One-Pass Trajectory Compression~\cite{LinMZWH17}}.  Trajectory compression (also known as trajectory simplification) is to compress data points in a trajectory to a set of continuous line segments, and is commonly used  in practice.

@@

An \lsa algorithm is {\em one-pass} if it processes each point in a trajectory once and only once when compressing the trajectory.
Obviously, one-pass algorithms have low time and space complexities, and are more appropriate for online processing, and
the difficulty comes from the need to achieve effective compression ratios.
Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker} and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window. That is to say, whenever a new directed line segment is formed, these algorithms always check its distances to all or a subset of data points, and, therefore, a data point is checked multiple times, depending on its order in the trajectory and the number of directed line segments formed. Hence, {\em an appropriate local distance checking approach is needed in the first place for designing one-pass trajectory simplification algorithms}.

 We develop a  fitting function such that a data point is checked only once during the entire process of trajectory simplification. Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms that scan each data point in a trajectory once and only once. By comparing our algorithms with \fbqsa (\emph{the fastest} existing \lsa algorithm) and \dpa (the {\em best} existing \lsa algorithm in terms of {\em compression ratio}). We find that algorithms are more than four times faster than \fbqsa, and have  comparable compression ratios with \dpa.

\stitle{(2) Dense Temporal Subgraph Computation~\cite{MaHWLH17}}. Dense subgraph discovery and analysis have been widely studied in static networks, such as  finding maximal cliques, k-core analysis and  the Prize Collecting Steiner Tree problem. It is worth pointing out that dense subgraphs are a very general concept, and their concrete semantics highly depend on the studied problems and applications. How to properly transfer or define their semantics over to temporal networks is still in the early stage, not to mention effective and efficient analytic algorithms.

We investigate a special class of temporal networks (see a recent survey \cite{tn-survey}) such that their nodes and edges are kept fixed, but their edge weights constantly and regularly vary with timestamps. Essentially, a temporal network with $T$ timestamps can be viewed as $T$ snapshots of a static network such that the network nodes and edges are kept the same among these $T$ snapshots, while the edge weights vary with network snapthots.
%
Road traffic networks typically fall into this category, and  road traffic analyses are of particular importance for large cities, such as Beijing, New York, London and Paris, that are facing with heavy traffic congestions, one of the great challenges of urban computing.

We also focus on a certain form of dense temporal subgraphs, which was initially studied in \cite{BogdanovMS11}.
Formally speaking, a temporal subgraph corresponds to a connected subgraph measured by the sum of all its edge weights in a time interval, \ie  a continuous sequence of timestamps. Intuitively, a dense subgraph that we consider  corresponds to a  collection of connected highly slow or jam roads (\ie  a jam area) in road networks, lasting for a continuous sequence of snapshots.

However, the problem of  finding dense subgraphs in temporal networks is non-trivial, and it is already \NP-complete even for a temporal network with a single snapshot and with $+1$ or $-1$ edge weights only, as observed in \cite{BogdanovMS11}. Even worse, it remains hard to approximate for temporal networks  with single snapshots. Moreover, given a temporal network with $T$ timestamps, there are a total number of $T*(T+1)/2$ time intervals to consider, which further aggravates the difficulty. Finally, the state of the art solution {\sc meden} \cite{BogdanovMS11} adopts a filter-and-verification framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}. Hence, {\sc meden} is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.

 a highly efficient and effective data-driven approach, instead of filter-and-verification, which employs hidden data statistics to find dense temporal subgraphs in large temporal networks.  data-driven approach to identifying $k$ time intervals from a total of $T*(T+1)/2$ ones, striking a balance between quality and efficiency, in which $T$ is the number of snapshots and $k$ is a small constant, \eg 10. This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on a novel {\em evolving convergence phenomenon}~\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}.

Using both real-life and synthetic data, we conduct an extensive experimental study.
(a) We find that the dense subgraphs found by our method {\sc FIDES} have the best quality, \ie about 100.20\% and 100.15\% on average of those found by the state of the art solution {\sc meden}~\cite{BogdanovMS11}, respectively.
(b) Our method {\sc FIDES} is  on average 2,980 and 1,486 times  faster than {\sc meden}, respectively.
(c) Finally, {\sc meden} already ran out of memory for temporal graphs with 150,000 nodes and 2,000 snapshots only.

Temporal network -> dynamic road network -> dense temporal subgraph (definition) -> time interval (FAV)- not big data friendly

Temporal network analysis
has recently attracted more and more attentions

>>>>

\stitle{(2) One-Pass Trajectory Compression~\cite{LinMZWH17}}.  Trajectory compression (also known as trajectory simplification) is to compress data points in a trajectory to a set of continuous line segments, and is commonly used  in practice.

@@

An \lsa algorithm is {\em one-pass} if it processes each point in a trajectory once and only once when compressing the trajectory.
Obviously, one-pass algorithms have low time and space complexities, and are more appropriate for online processing, and
the difficulty comes from the need to achieve effective compression ratios.
Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker}) and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window. That is to say, whenever a new directed line segment is formed, these algorithms always check its distances to all or a subset of data points, and, therefore, a data point is checked multiple times, depending on its order in the trajectory and the number of directed line segments formed. Hence, {\em an appropriate local distance checking approach is needed in the first place for designing one-pass trajectory simplification algorithms}.

 We develop a  fitting function such that a data point is checked only once during the entire process of trajectory simplification. Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms that scan each data point in a trajectory once and only once. By comparing our algorithms with \fbqsa (\emph{the fastest} existing \lsa online algorithm \cite{Liu:BQS}) and \dpa (the {\em best} existing \lsa batch algorithm in terms of {\em compression ratio} \cite{Douglas:Peucker}), our one-pass algorithms are over four times faster than \fbqsa, and have  comparable compression ratios with \dpa.

\stitle{(3) Dense Temporal Subgraph Computation~\cite{MaHWLH17}}.  We study dense subgraphs in {\em a special type of temporal networks} such that their nodes and edges are kept fixed, but their edge weights constantly and regularly vary with timestamps~\cite{MaHWLH17}.  Essentially, a temporal network with $T$ timestamps can be viewed as $T$ snapshots of a static network such that the network nodes and edges are kept the same among these $T$ snapshots, while the edge weights vary with network snapthots. Road traffic networks typically fall into this category of temporal networks, and dense subgraphs are used for road traffic analyses that are of particular importance for large cities, such as Beijing, New York, London and Paris, that are facing with heavy traffic congestions, one of the great challenges of urban computing.

Dense subgraphs are a general concept, and their concrete semantics highly depend on the studied problems and applications. Though  dense subgraph discovery and analysis have been widely studied in static networks, how to properly transfer or define their semantics over to temporal networks is still in the early stage, not to mention effective and efficient analytic algorithms.

We adopt the {\em form of dense temporal subgraphs} initially defined and studied in \cite{BogdanovMS11}, such that a temporal subgraph corresponds to a connected subgraph measured by the sum of all its edge weights in a time interval, \ie  a continuous sequence of timestamps. Intuitively, a dense subgraph that we consider  corresponds to a  collection of connected highly slow or jam roads (\ie  a jam area) in road networks, lasting for a continuous sequence of snapshots.

The problem of  finding dense subgraphs in temporal networks is non-trivial, and it is already \NP-complete even for a temporal network with a single snapshot and with $+1$ or $-1$ edge weights only, as observed in \cite{BogdanovMS11}. Even worse, it remains hard to approximate for temporal networks  with single snapshots.
Moreover, given a temporal network with $T$ timestamps, there are a total number of $T*(T+1)/2$ time intervals to consider, which further aggravates the difficulty.

The state of the art solution {\sc meden} \cite{BogdanovMS11} adopts a filter-and-verification framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}. This is not big data friendly, and it is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.

We develop a data-driven approach, instead of filter-and-verification, to  identifying the most possible $k$ time intervals from $T \times (T + 1)/2$ time intervals, in which $T$ is the number of snapshots and k is a small constant, \eg 10. This is achieved by exploring the characteristics of time intervals involved with dense subgraphs based on the observation of {\em evolving convergence phenomenon} in traffic data, inspired by the convergent evolution in nature~\footnote{\small \url{https://en.wikipedia.org/wiki/Convergent_evolution}}. Using both real-life and synthetic data, we experimentally show that Our method {\sc fides} is over 1000 times faster than the state of the art solution {\sc meden}~\cite{BogdanovMS11}, while the quality of dense subgraphs found is comparable with {\sc meden}.
